Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-06-19 analysis/paper/paper.Rnw
removed more unnecessary packages
fixed spacing issue with session_info()

\documentclass[]{article}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\linenumbers

\usepackage{bbm}
\usepackage{setspace}
\usepackage[left = 1in, right = 1in, top = 1.5in, bottom = 1in]{geometry}
\usepackage{multirow}
\usepackage{float}
\usepackage{newfloat}
\usepackage{multicol}
%\usepackage[lite]{mtpro2} %contains \widetilde
\usepackage[titletoc]{appendix}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{unicode=true,
%            pdftitle={Chapter 1},
%            pdfauthor={Frederick Boehm},
%            pdfborder={0 0 0},
            colorlinks=true,
            breaklinks=true}
\usepackage[yyyymmdd,hhmmss]{datetime}

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl, xcolor}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
\usepackage{etoolbox} % for messing with page style & title pages
%\usepackage{fancyhdr}
%\setlength{\headheight}{15.2pt}
%\pagestyle{fancyplain}
%\fancyhf{}
%\lhead{}
%\chead{}
%\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
%\rfoot{Compiled on \today\ at \currenttime}
%\renewcommand{\headrulewidth}{0pt} % remove top line
%\renewcommand{\footrulewidth}{0pt} % remove bottom line
%\renewcommand{\headrule}{}%

@@

@@

<<setup, include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = TRUE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE)
@

\doublespacing
\listoftodos
\tableofcontents
\listoffigures
\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\section{Introduction}

@@

@@

>>>>

\documentclass[]{article}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{bbm}
\usepackage[left = 1in, right = 1in, top = 1.5in, bottom = 1in]{geometry}
%\usepackage[titletoc]{appendix}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{unicode=true,
%            pdftitle={Chapter 1},
%            pdfauthor={Frederick Boehm},
%            pdfborder={0 0 0},
            colorlinks=true,
            breaklinks=true}
\usepackage[yyyymmdd,hhmmss]{datetime}

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
%\usepackage{etoolbox} % for messing with page style & title pages
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}%

@@

\doublespacing

@@

<<setup, include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = TRUE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE)

options(tinytex.verbose = TRUE)
@

\listoftodos
\tableofcontents
\listoffigures
\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\section{Introduction}

@@

\begin{singlespacing}

@@

\end{singlespacing}
